Figures and results for main manuscript

### 2021-05-09 analysis/reports/submission2/appendices/s10_very_small_results.Rmd
this looks good to me

  if(grepl("sim_pos", col_name)) {
    xvarname = "Mean dissimilarity"
    min_nparts = 40
  } else {
    min_nparts = 20
    xvarname = "Breadth index"
  }

@@

```{r, fig.dim = c(6,8)}

@@

```{r, fig.dim = c(6,8)}

nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best", "Dissimilarity to the central tendency") +
  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
  xlab("Mean dissimilarity of elements of feasible set to central tendency") +
  ylab("Number of communities") +
  ggtitle("")

>>>>

  if(grepl("sim_pos", col_name)) {
xvarname = "95th percentile \nof dissimilarity scores"
min_nparts = 40
  } else {
    min_nparts = 20
    xvarname = "Breadth index"
  }

@@

```{r, fig.dim = c(5,6)}

@@

```{r, fig.dim = c(5,6)}

nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best_95", "Dissimilarity to the central tendency") +
  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
  xlab("95th percentile of scores for dissimilarity to the central tendency \nfor elements of the feasible set") +
  ylab("Number of communities") +
  ggtitle("")

### 2021-05-09 analysis/reports/submission2/appendices/s4_dissimilarity_fig.Rmd
this looks good to me

```{r, fig.dim = c(7,7)}
ggplot(all_di, aes(sim_pos_from_best, real_po, color = `Observed \npercentile score`)) +
  geom_point(alpha = .3) +
  geom_point(data = filter(all_di, s0 < 0)) +
  geom_abline(slope = 1, intercept = 0) +
  scale_color_viridis_d(end = .8, direction = -1) +
  xlab("Mean of elements from feasible set") +
  ylab("Observed value") +
  ggtitle("Dissimilarity to the central tendency") +  theme(legend.position = "bottom")+
  facet_wrap(vars(Dataset))
#,
#
#
# ggplot(filter(all_di, nparts < 10 ^ 50), aes(nparts, sim_pos_from_best, color = Dataset)) +
#   geom_point(alpha = .3) +
#   geom_point(data = filter(all_di, s0 < 0)) +
#   scale_color_viridis_d(end = .9) +
#   xlab("Number of elements in the feasible set") +
#   ylab("Mean dissimilarity of feasible set to central tendency") +
#   scale_x_log10() +
#   ggtitle("Over the size of the feasible set")
# ), ncol = 1,
#top = textGrob("Dissimilarity to central tendency"))

**Figure S4**. Dissimilarity of observed and sampled SADs to the central tendency of the feasible set. Observed SADs are often much more dissimilar to the central tendency of their feasible sets (y-axis) than the mean dissimilarity of samples from the feasible set and the central tendency (x-axis). Dissimilarity can range from 0-1. The black line is the 1:1 line. Of observed SADs that are more disssimilar to the central tendency than are 95% of samples from the feasible set (green points), the absolute increase in dissimlarity ranges from .04 to .6. These observed SADs are from 1.4 to 9.7 times more dissimilar to the central tendency than the maen of samples from the feasible set.

>>>>

```{r, fig.dim = c(7,5)}
ggplot(all_di, aes(sim_pos_from_best, real_po)) +
  geom_point(alpha = .05) +
  geom_point(data = filter(all_di, s0 < 0)) +
  geom_abline(slope = 1, intercept = 0) +
  scale_color_viridis_d(end = .8, direction = -1) +
  xlab("95th percentile for elements from feasible set") +
  ylab("Observed value") +
  ggtitle("Dissimilarity to the central tendency") +  theme(legend.position = "bottom")+
  facet_wrap(vars(Dataset))
#,
#
#
# ggplot(filter(all_di, nparts < 10 ^ 50), aes(nparts, sim_pos_from_best, color = Dataset)) +
#   geom_point(alpha = .3) +
#   geom_point(data = filter(all_di, s0 < 0)) +
#   scale_color_viridis_d(end = .9) +
#   xlab("Number of elements in the feasible set") +
#   ylab("Mean dissimilarity of feasible set to central tendency") +
#   scale_x_log10() +
#   ggtitle("Over the size of the feasible set")
# ), ncol = 1,
#top = textGrob("Dissimilarity to central tendency"))
increase <- all_di %>% filter(real_po_percentile_excl > 95) %>% mutate(difference = real_po - sim_pos_from_best_95, ratio = real_po / sim_pos_from_best_95)
```

**Figure S4**. Dissimilarity of observed and sampled SADs to the central tendency of the feasible set. Observed SADs are often much more dissimilar to the central tendency of their feasible sets (y-axis) than the 95th percentile dissimilarity of samples from the feasible set and the central tendency (x-axis). Dissimilarity can range from 0-1. The black line is the 1:1 line. Of observed SADs that are more disssimilar to the central tendency than are 95% of samples from the feasible set, the absolute increase in dissimlarity ranges from ```r round(min(increase$difference), 4)``` to ```r round(max(increase$difference), 3)```. These observed SADs are from ```r round(min(increase$ratio), 3)``` to ```r round(max(increase$ratio), 2)``` times more dissimilar to the central tendency than the 95th percentile of dissimilarity scores for samples from the feasible set.

### 2021-05-09 analysis/reports/submission2/appendices/s6_breadth_index_fig.Rmd
this looks good to me

  if(grepl("sim_pos", col_name)) {
    xvarname = "Mean dissimilarity"
    min_nparts = 40
  } else {
    min_nparts = 20
    xvarname = "Breadth index"
  }

@@

```{r, fig.dim = c(10,5)}

@@

**Figure S6**. Partially because of the uneven distribution of S and N among the different datasets, the narrowness of the feasible sets - defined either as the mean dissimilarity of samples from the feasible set to the central tendency of the feasible set, or using a breadth index for specific metrics - varies among different datasets. In particular, the FIA dataset, and subsets of the Mammal Community and Miscellaneous Abundance databases, often have highly variable, broadly-defined statistical baselines derived from the feasible set.

>>>>

  if(grepl("sim_pos", col_name)) {
    xvarname = "95th percentile \nof dissimilarity scores"
    min_nparts = 40
  } else {
    min_nparts = 20
    xvarname = "Breadth index \n"
  }

@@

```{r, fig.dim = c(10,5.5)}

@@

**Figure S6**. Partially because of the uneven distribution of S and N among the different datasets, the narrowness of the feasible sets - defined either as the 95th percentile of scores for the dissimilarity of samples from the feasible set compared to the central tendency of the feasible set, or using a breadth index for specific metrics - varies among different datasets. In particular, the FIA dataset, and subsets of the Mammal Community and Miscellaneous Abundance databases, often have highly variable, broadly-defined statistical baselines derived from the feasible set.

### 2021-05-09 analysis/reports/submission2/appendices/s7_complete_resampling_results.Rmd
this looks good to me

  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
    geom_histogram(bins = 40, boundary = 100) +
    theme_bw() +
    xlab("") +
    ylab("") +
    geom_vline(xintercept = cutoff_percentiles, color = "red") +
    ggtitle( plot_name) +
    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
    theme(plot.title = element_text(size=10))

@@

  ggplot(di_df, aes(nparts, response, color = Dataset)) +
    geom_point(data = filter(di_df, dat == "fia"), alpha = .1) +
    geom_point(data = filter(di_df, dat != "fia"), alpha = .1) +
    geom_point(data = filter(di_df, s0 < 0)) +
    scale_color_viridis_d(end = .9) +
    xlab("") +
    ylab(ylabel) +
    scale_x_log10() +
    ggtitle(yvar_name) +
    theme(legend.position = "none")+
    theme(plot.title = element_text(size=10))
}

plot_narrowness_legend <- function(di_df) {

  legend_df <- di_df %>%
    select(Dataset) %>%
    distinct() %>%
    mutate(ymark = dplyr::row_number())

  ggplot(legend_df, aes(1, ymark, color = Dataset)) +
    geom_label(aes(x = 2, y = ymark, label = Dataset)) +
    geom_point(size = 4) +
    scale_color_viridis_d(end = .9) +
    xlab("") +
    ylab("") +
    theme(legend.position = "none") +
    xlim(1, 3) + theme(
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.y = element_blank(),
      panel.grid.minor.y = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank()
    ) +
    ggtitle("Dataset")

}
#
# gridExtra::grid.arrange(grobs = list(
#   plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity to central tendency"),
#   plot_narrowness_legend(all_di)),
#   ncol = 1)
```

plot_narrowness_hist <- function(di_df, col_name, plot_name, facetvar = "Dataset", min_s0 = 0) {

  if(grepl("sim_pos", col_name)) {
    xvarname = "Mean dissimilarity"
    min_nparts = 40
  } else {
    min_nparts = 20
    xvarname = "Breadth index"
  }

  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
    geom_histogram(bins = 40, boundary = 100) +
    theme_bw() +
    ylab("") +
    xlab(xvarname) +
    ggtitle( plot_name) +
    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
    theme(plot.title = element_text(size=10))

@@

```{r, fig.dim = c(8,6)}
gridExtra::grid.arrange(grobs = list(
  ggplot(filter(rs_results_long, !grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
  geom_point() +
  facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
  scale_color_viridis_d(end = .8) +
  ylab("Proportion of extreme observed values") +ylim(0, .7) +
  xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
  ggplot(filter(rs_results_long, grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
  geom_point() +
  facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
  scale_color_viridis_d(end = .8) +
  ylab("") +
  xlab("") + ylim(0, .7) +
  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))
```

@@

```{r, fig.dim = c(8,6)}
gridExtra::grid.arrange(grobs = list(
  ggplot(filter(rs_results_long, !grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
  geom_point() +
  facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
  scale_color_viridis_d(end = .8) +
  ylab("Proportion of extreme observed values") +ylim(0, .7) +
  xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
  ggplot(filter(rs_results_long, grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
  geom_point() +
  facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
  scale_color_viridis_d(end = .8) +
  ylab("") +
  xlab("") + ylim(0, .7) +
  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))

>>>>

  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
    geom_histogram(bins = 40, boundary = 100) +
    theme_bw() +
    xlab("") +
    ylab("") +
    geom_vline(xintercept = cutoff_percentiles, color = "red") +
    ggtitle( plot_name) +
    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
    theme(plot.title = element_text(size=9), plot.margin=unit(c(1, 0, -5, -1), units = "mm"), axis.text = element_text(size = 6), strip.text = element_text(size = 7), strip.placement = "inside") +
    scale_y_continuous(n.breaks = 3)

@@

  ggplot(di_df, aes(nparts, response, color = Dataset)) +
    geom_point(data = filter(di_df, dat == "fia"), alpha = .1) +
    geom_point(data = filter(di_df, dat != "fia"), alpha = .1) +
    geom_point(data = filter(di_df, s0 < 0)) +
    scale_color_viridis_d(end = .9) +
    xlab("") +
    ylab(ylabel) +
    scale_x_log10() +
    ggtitle(yvar_name) +
    theme(legend.position = "none")+
    theme(plot.title = element_text(size=10)) +
    scale_y_continuous(nbreaks =3)
}
```

@@

```{r, fig.dim = c(8,4)}
gridExtra::grid.arrange(grobs = list(
  ggplot(filter(rs_results_long, !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
  geom_point() +
  facet_wrap(vars(Dataset), scales = "fixed", ncol =5) +
  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
  scale_color_viridis_d(end = .8, option = "plasma") +
  ylab("Proportion of extreme \nobserved values") + xlab("") +ylim(0, .7) + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90), plot.margin = unit(c(5, 5, 2, 2), units = "mm"))))

@@

```{r, fig.dim = c(8,4)}
gridExtra::grid.arrange(grobs = list(
  ggplot(filter(rs_results_long, weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
  geom_point() +
  facet_wrap(vars(Dataset), scales = "fixed", ncol =5) +
  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
  scale_color_viridis_d(end = .8, option = "plasma") +
  ylab("Proportion of extreme \nobserved values") + xlab("") +ylim(0, .7) + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90), plot.margin = unit(c(5, 5, 2, 2), units = "mm"))))

### 2021-05-09 analysis/reports/submission2/manuscript_main_rev.Rmd
this looks good to me

  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
    geom_histogram(bins = 100, boundary = 100) +
    theme_bw() +
    xlab("") +
    ylab("") +
    geom_vline(xintercept = cutoff_percentiles, color = "red") +
    ggtitle( plot_name) +
    #geom_text(data = distinct(select(di_df, Dataset)), aes(x = 45, y = 100, label = Dataset)) +
    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
    theme(plot.title = element_text(size=9), plot.margin=unit(c(1, 0, -5, -3), units = "mm"), axis.text = element_text(size = 6), strip.text = element_text(size = 7), strip.placement = "inside") +
    scale_y_continuous(n.breaks = 3)

@@

  plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity", facetvar = "Dataset", tails = 1),
  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "Proportion of rare species", facetvar = "Dataset"),
  plot_percentile_hist(all_di, "skew_percentile_mean", "Skewness", facetvar = "Dataset", min_s0 = 3) + theme(plot.margin = unit(c(1, 2, -5, -5), units = "mm")),
  plot_percentile_hist(all_di, "simpson_percentile_mean", "Simpson evenness", facetvar = "Dataset"),
  plot_percentile_hist(all_di, "shannon_percentile_mean", "Shannon diversity", facetvar = "Dataset")
), ncol = 3, 
left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
bottom = textGrob("Percentile rank of observed value relative to feasible set"), 
gp = gpar(fill = "white"))

@@

  ggplot(di_df, aes(nparts, response, color = Dataset)) +
    geom_point(data = filter(di_df, dat == "fia"), alpha = .1) +
    geom_point(data = filter(di_df, dat != "fia"), alpha = .1) +
    geom_point(data = filter(di_df, s0 < 0)) +
    scale_color_viridis_d(end = .9) +
    xlab("") +
    ylab(ylabel) +
    scale_x_log10() +
    ggtitle(yvar_name) +
    theme(legend.position = "none")+
    theme(plot.title = element_text(size=10)) +
    theme(legend.text = element_text(size = 8), plot.margin = unit(c(0, 10, 0, 0), units = "mm"), axis.text = element_text(size = 7))
}

@@

fig_4 <- gridExtra::grid.arrange(grobs = list(
  plot_narrowness(all_di, "sim_pos_from_best_95", "Dissimilarity") + ylab("Dissimilarity \n95th percentile"),
    plot_narrowness(all_di, "skew_95_ratio_2t", "Skewness") + ylab("\nBreadth index"),
    plot_narrowness(all_di, "simpson_95_ratio_2t", "Simpson evenness")+ ylab("\nBreadth index"),
    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "Proportion of rare species")+ ylab("\nBreadth index"),
       plot_narrowness(all_di, "shannon_95_ratio_2t", "Shannon diversity")+ ylab("\nBreadth index")+ theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.margin = margin(-.3,0,0,0, unit = "in"),legend.key.size = unit(.25, units = "mm"), legend.title = element_text(size = 8))), ncol = 1, bottom = textGrob("Number of elements in the feasible set"))

@@

}
all_di <- all_di %>%
  mutate( `Number of elements` = ifelse(nparts < 2000, "Less than 2000", "More than 2000"))
diss_results <- all_di %>%
  filter(nparts > 20) %>%
  group_by(Dataset,  `Number of elements` ) %>%
  summarize(high_diss = mean(real_po_percentile_excl > 95),
            nsites = dplyr::n()) %>%
  ungroup() %>%
  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
  select(-nsites)

@@

nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb")), "skew_95_ratio_2t", "Skewness") +
  facet_wrap(vars(`Number of elements`, Dataset_short), scales = "free_y", nrow = 2, ncol = 2) +
  xlab("Breadth index") +
  ylab("Number of communities") +
  ggtitle("Skewness") + theme(plot.margin = unit(c(0,5,0,2), units = "mm"), axis.text = element_text(size = 6) ,strip.text = element_text(size = 7), strip.placement = "inside")

phist <- plot_percentile_hist_small(filter(all_di, dat %in% c("fia", "mcdb")), "skew_percentile_mean", "Skewness")  +
  facet_wrap(vars(`Number of elements`, Dataset_short), scales = "free_y", nrow = 2, ncol = 2) +
  xlab("Percentile rank of observed value \nrelative to feasible set") +
  ylab("Number of communities") +
  ggtitle("Skewness")+ theme(plot.margin = unit(c(0,5,5,2), units = "mm"), plot.title = element_text(size = 10))

@@

ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 80, height = 150, dpi = 800, units = "mm")

@@

rs_results_long <- left_join(rs_results_long, metric_names)
#
# ggplot(filter(rs_results_long, !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
#   geom_point() +
#   facet_wrap(vars(Dataset), scales = "fixed", ncol = 1) +
#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
#   scale_color_viridis_d(end = .8) +
#   ylab("Proportion of extreme observed values") +
#   xlab("")
# 
# fig_5 <- gridExtra::grid.arrange(grobs = list(
#   ggplot(filter(rs_results_long, !grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
#   geom_point() +
#   facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
#   scale_color_viridis_d(end = .8, option = "plasma") +
#   ylab("Proportion of extreme observed values") +ylim(0, .7) +
#   xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
#   ggplot(filter(rs_results_long, grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
#   geom_point() +
#   facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
#   scale_color_viridis_d(end = .8, option = "plasma") +
#   ylab("") +
#   xlab("") + ylim(0, .7) +
#   theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"), top = textGrob("Figure 5"))

fig_5 <- gridExtra::grid.arrange(grobs = list(
  ggplot(filter(rs_results_long, !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
  geom_point() +
  facet_wrap(vars(Dataset), scales = "fixed", ncol =5) +
  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
  scale_color_viridis_d(end = .8, option = "plasma") +
  ylab("Proportion of extreme observed values") +ylim(0, .7) +
  xlab("Metric") + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90), plot.margin = unit(c(60, 0, 0, 0), units = "mm"))))

ggsave("figure_5.pdf", device = "pdf", plot = fig_5, width = 180, height =
180, dpi = 800, units = "mm")
# 
# pdf("figure_5.pdf", bg = "white", paper = "letter", width = 6, height = 5)
# fig_5
# dev.set(dev.next())
# while (!is.null(dev.list()))  dev.off()
#

>>>>

  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
    geom_histogram(bins = 40, boundary = 100) +
    theme_bw() +
    xlab("") +
    ylab("") +
    geom_vline(xintercept = cutoff_percentiles, color = "red") +
    ggtitle( plot_name) +
    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
    theme(plot.title = element_text(size=9), plot.margin=unit(c(1, 0, -5, -1), units = "mm"), axis.text = element_text(size = 6), strip.text = element_text(size = 7), strip.placement = "inside") +
    scale_y_continuous(n.breaks = 3)

@@

  plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity", facetvar = "Dataset", tails = 1),
  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "Proportion of rare species", facetvar = "Dataset"),
  plot_percentile_hist(all_di, "skew_percentile_mean", "Skewness", facetvar = "Dataset", min_s0 = 3) + theme(plot.margin =unit(c(1, 3, -5, -1), units = "mm")),
  plot_percentile_hist(all_di, "simpson_percentile_mean", "Simpson evenness", facetvar = "Dataset"),
  plot_percentile_hist(all_di, "shannon_percentile_mean", "Shannon diversity", facetvar = "Dataset")
), ncol = 3, 
left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
bottom = textGrob("Percentile rank of observed value relative to feasible set"), 
gp = gpar(fill = "white"))

@@

  ggplot(di_df, aes(nparts, response, color = Dataset)) +
    geom_point(data = filter(di_df, dat == "fia"), alpha = .1) +
    geom_point(data = filter(di_df, dat != "fia"), alpha = .1) +
    geom_point(data = filter(di_df, s0 < 0)) +
    scale_color_viridis_d(end = .9) +
    xlab("") +
    ylab(ylabel) +
    scale_x_log10() +
    ggtitle(yvar_name) +
    theme(legend.position = "none")+
    theme(plot.title = element_text(size=10)) +
    theme(legend.text = element_text(size = 8), plot.margin = unit(c(0, 10, 0, 2), units = "mm"), axis.text = element_text(size = 7))
}

@@

fig_4 <- gridExtra::grid.arrange(grobs = list(
  plot_narrowness(all_di, "sim_pos_from_best_95", "Dissimilarity") + ylab("Dissimilarity \n95th percentile") + theme(plot.margin =unit(c(1, 10, 0, 2), units = "mm") ),
    plot_narrowness(all_di, "skew_95_ratio_2t", "Skewness") + ylab("\nBreadth index"),
    plot_narrowness(all_di, "simpson_95_ratio_2t", "Simpson evenness")+ ylab("\nBreadth index"),
    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "Proportion of rare species")+ ylab("\nBreadth index"),
       plot_narrowness(all_di, "shannon_95_ratio_2t", "Shannon diversity")+ ylab("\nBreadth index")+ theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.margin = margin(-.3,0,0,0, unit = "in"),legend.key.size = unit(.25, units = "mm"), legend.title = element_text(size = 8))), ncol = 1, bottom = textGrob("Number of elements in the feasible set"))

@@

}
all_di <- all_di %>%
  mutate( `Number of elements` = ifelse(nparts < 2000, "Less than 2000 possible SADs", "More than 2000 possible SADs"))
diss_results <- all_di %>%
  filter(nparts > 20) %>%
  group_by(Dataset,  `Number of elements` ) %>%
  summarize(high_diss = mean(real_po_percentile_excl > 95),
            nsites = dplyr::n()) %>%
  ungroup() %>%
  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
  select(-nsites)

@@

nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_95_ratio_2t", "Skewness") +
  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
  xlab("Breadth index") +
  ylab("Number of communities") +
  ggtitle("Skewness") + theme(plot.margin = unit(c(0,5,0,2), units = "mm"), axis.text = element_text(size = 6) ,strip.text = element_text(size = 7), strip.placement = "inside")

phist <- plot_percentile_hist_small(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_percentile_mean", "Skewness")  +
  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
  xlab("Percentile rank of observed value \nrelative to feasible set") +
  ylab("Number of communities") +
  ggtitle("Skewness")+ theme(plot.margin = unit(c(0,5,5,2), units = "mm"), plot.title = element_text(size = 10))

@@

ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 180, height = 150, dpi = 800, units = "mm")

@@

rs_results_long <- left_join(rs_results_long, metric_names) %>%
  mutate(Dataset_short = ifelse(Dataset == "FIA", "FIA", 
                                ifelse(Dataset == "Breeding Bird Survey", "BBS", 
                                       ifelse(Dataset == "Mammal Communities", "Mammals", ifelse(Dataset == "Gentry", "Gentry", "Misc.")))))

fig_5 <- gridExtra::grid.arrange(grobs = list(
  ggplot(filter(rs_results_long, !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
  geom_point() +
  facet_wrap(vars(Dataset_short), scales = "fixed", ncol =5) +
  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
  scale_color_viridis_d(end = .8, option = "plasma") +
  ylab("Proportion of extreme \nobserved values") + xlab("") +ylim(0, .7) + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90), plot.margin = unit(c(5, 5, 2, 2), units = "mm"))))

ggsave("figure_5.pdf", device = "pdf", plot = fig_5, width = 180, height =
80, dpi = 800, units = "mm")
# 
# pdf("figure_5.pdf", bg = "white", paper = "letter", width = 6, height = 5)
# fig_5
# dev.set(dev.next())
# while (!is.null(dev.list()))  dev.off()
#
